---
title: "Resumes: Courage and Temperance"
format:
  html: default
execute:
  echo: false
---

```{r}
#| label: setup
#| message: false

library(tidyverse)
library(tidymodels)
library(broom)
library(marginaleffects)

resumes <- read_csv("data/resumes.csv", show_col_types = FALSE) |>
  mutate(call = as.factor(call))
```

## The Question

Bertrand and Mullainathan (2004) sent 4,870 fictitious resumes to help-wanted ads in Boston and Chicago newspapers, randomly assigning each resume an African-American-sounding or White-sounding name. Our data records, for each resume, whether it received a callback, along with the name's connotation and the resume's characteristics.

Imagine that you work for a civil rights organization in Chicago. You want to understand the process by which black US citizens are discriminated against in hiring today.

The civil rights organization asks: What is the average causal effect of having a black-sounding name, rather than a white-sounding name, on the probability that a job applicant in Chicago today receives a callback?

The setup chunk of this document loads the packages and the data. Today covers both Courage and Temperance, so the modeling and the answering happen in one meeting.

## Courage

### Candidate Models

Estimate a model in which `call` is the outcome and `city` is the only covariate.

```{r}
logistic_reg() |>
  fit(call ~ city, data = resumes) |>
  tidy(conf.int = TRUE) 
```

Display the coefficients and their confidence intervals.





Interpret the estimate for `citychicago`.



Estimate a model in which `call` is the outcome and `city` and `ethnicity` are the covariates.

```{r}
logistic_reg() |>
  fit(call ~ city + ethnicity, data = resumes) |>
  tidy(conf.int = TRUE) 
```

Display the coefficients and their confidence intervals.



Interpret the estimate for `ethnicitycauc`.



Add `quality`, and its interaction with `ethnicity`, to the previous model.



Display the coefficients and their confidence intervals.



Interpret the estimate for the interaction `ethnicitycauc:qualitylow`.



### The Data Generating Mechanism

Which model should we choose, and why? Define `fit_resumes` as your chosen model.

```{r}
fit_resumes <- logistic_reg() |>
  fit(call ~ city + ethnicity + experience, data = resumes)

tidy(fit_resumes, conf.int = TRUE)
```


------------------------------------------------------------------------

## Temperance

### Predictions

Use `predictions(fit_resumes, type = "prob")` to estimate the callback probability for individual resumes in the sample.

```{r}
predictions(fit_resumes, type = "prob") |>
  as_tibble() |>
  filter(group== "yes") 
```



### Visualizations

Create a visualization of the average predictions by ethnicity using `plot_predictions()`.

```{r}
plot_predictions(fit_resumes, by = "ethnicity", type = "prob", 
                 conf_level = 0.95) +
  labs(title = "Callback Probability by Ethnicity (with 95% CI)",
       y = "Predicted Callback Probability",
       x = "Ethnicity") +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5),
        panel.grid.major = element_line(color = "gray90"))
```



What measure of uncertainty is shown in this plot?



------------------------------------------------------------------------
